---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Looking at workplace uniform preferences across shift durations 

This survey looked at workplace uniform preferences and whether or not the duration of an individuals shift is likely to influence what they prefer to wear to work 

The 'uniform' of the workplace in question is more of a restriction to specific articles of clothing and their colors (i.e., a black or white t-shirt, blouse, button-up or the company graphic tee, and black dress pants, fitted jeans or medium to long length skirts) - rather than a set outfit. 

```{r}
library(tidyverse)

logged_data <- data_frame(read.csv("Uniform Responses.csv")) # Loading in the data 

logged_data <- logged_data %>%      # renaming the variables 
  rename(Style.Top = What.style.of.top.are.you.wearing., 
         Style.Pant = What.style.of.pants.are.you.wearing.,
         Shift.Hrs = How.many.hours.is.your.shift.today.)

Mean_Shift <- logged_data$Shift.Hrs %>%  # The average shift length 
  mean()+ 
  round(1)

Min_Shift <- logged_data$Shift.Hrs %>% # The shortest shift recorded 
  min()

Max_Shift <- logged_data$Shift.Hrs %>% # The longest shift recorded
  max()

paste0("The shortest shift was ",Min_Shift,", while the longest shift recorded was ",Max_Shift,".")
```

### Looking at top style across shift duration 
```{r fig.width=8, fig.height=4}
logged_data %>%   # Looking at how the styles of tops worn change across shift duration
  ggplot()+ 
  geom_bar(aes(x = Shift.Hrs, 
               fill = Style.Top)) +
  labs(title = "Style of Top Worn Across Shift Lengths", 
       x = "Shift Length (hrs)", 
       y = "Tops Worn") + 
  theme_linedraw() 
```

When looking at this bar chart we can see that t-shirts and graphic tees are the two most popular options. Along with this, these two styles of tops where the only to be worn during shifts that were 7 hours or shorter, and that blouses and button-ups were exclusively seen in shifts which were over 8 hours. This is possible due to fact the causal or part-time workers are more likely to wear a relaxed style of shirt, whilst full-time workers which include managers and higher up are more likely to opt for a style of shirt which is more formal. 


### Looking at pant style across shift duration 
```{r fig.width=8, fig.height=4}
logged_data %>%   # Looking at how the styles of pants worn change across shift duration
  ggplot()+ 
  geom_bar(aes(x = Shift.Hrs, 
               fill = Style.Pant)) +
  labs(title = "Style of Pants Worn Across Shift Lengths", 
       x = "Shift Length (hrs)", 
       y = "Pant Style") + 
  theme_linedraw()
```

When considering pant preferences we can see that jeans the most popular, and skirts are the least. Unlike the shirts there is not a super clear distinction in preference across shift hours. This is possibly because a nice black pair of jeans are able to be dressed up to be more formal and can also be more casual. 

